Distributions

### 2022-01-12 Ch2_distributions/Ch2_Figures.Rmd
Actually changing the order of the figures.

@@

@@

# Relative angle requires at least three consecutive observations since it is looking at changes in direction. Whereas, the absolute angle is just the direction of movement based on the absolute plane, and thus it only requires two consecutive observations. 
ptpl %>% 
  ungroup() %>% 
  mutate(individual = paste0("B", Bird_ID),
         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
  dplyr::select(individual, sgroup, rel.angle, abs.angle) -> angles_df
```

>>>>

# Figure 1 - Descriptions of the data

# To know the number of speed data points for each individual
# nonzerompm %>% group_by(Bird_ID) %>% count() %>% arrange(n)

# To know the number of speed data points per interval category
# nonzerompm %>% group_by(T_minutes) %>% count() %>% mutate(percent = n/nrow(nonzerompm))

@@

```{r eval=FALSE}
# Getting some data for the results
ptpl %>% group_by(burst) %>% add_tally(name = "burstn") %>% 
  dplyr::select(Bird_ID, burstn) %>% 
  filter(., burstn >=2) %>% 
  distinct() %>% #summary()
  ggplot(., aes(x = Bird_ID, y = burstn)) + 
  geom_boxplot()

@@

# Relative angle requires at least three consecutive observations since it is looking at changes in direction. Whereas, the absolute angle is just the direction of movement based on the absolute plane, and thus it only requires two consecutive observations. 
ptpl %>% 
  ungroup() %>% 
  mutate(individual = paste0("B", Bird_ID),
         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
  dplyr::select(individual, sgroup, rel.angle, abs.angle) -> angles_df

# Some info on the angles df

angles_df %>% 
  drop_na(rel.angle)
```
